True versus apparent shapes of astrophysical bow shocks

### 2016-05-06 papers/Paper1/sec-application.tex
Update conic-xi* figures and enhanced analysis

\begin{figure}
\includegraphics[width=\linewidth]{r-beta}
\caption{Bow shock shapes for interacting winds in the thin-shell
  approximation. Coordinates are normalized by $D$, the distance
  between the two wind sources.  The weaker source is at \((0.0, 0.0)\)
  and the stronger source is at \((1.0, 0.0)\).  Results are shown for
  different values of the wind momentum ratio, \(\beta\), and for the
  case where the weaker wind is isotropic (dashed lines) or an
  anisotropic proplyd photoevaporation flow (solid lines).}
\label{fig:r-beta}
\end{figure}

@@

@@

\begin{figure}
\includegraphics[width=\linewidth]{../../read-shapes/proplyd-shell-R0-Rc-cloud} 
\label{fig:prop-shell-rad}
\caption{Measurements of proplyd's characteristic radii $R_c$ and $R_0$. The curves represent a single bow shock with  fixed wind's momentum ratio $\beta$. 
The dots represent separations in inclination of $15^{\circ}$. The semitransparent curves represent bow shocks which the inner wind is isotropic and the full colored 
curves bow shocks which inner wind density decays as $\cos^{1/2}\theta$. The observational measurements are accompained with radial bars which represents the variations 
with a fraction of the shell's marks removed. Proplyds with less data marks or high asymmetry show higher deviations in the measurements.
%Our measures match far better than \citep{Robberto:2005}, but our data tend to lie at high inclinations $i \gtrsim 45^\circ$, when we expected the opposite. Right side: The same
}
\end{figure}

@@

With this we can use the results of section \ref{sec:conic} to estimate the projected conic shapes for bow shocks with different winds momenta and different density distributions. In figure () we show 
the theoretical conic curves for different vales of $\beta$ with a fixed $\xi$

>>>>

\begin{figure}
\includegraphics[width=\linewidth]{r-beta}
\caption{Bow shock shapes for interacting winds in the thin-shell
  approximation. Coordinates are normalized by $D$, the distance
  between the two wind sources.  The weaker source is at \((0.0, 0.0)\)
  and the stronger source is at \((1.0, 0.0)\).  Results are shown for
  different values of the wind momentum ratio, \(\beta\), and for the
  case where the weaker wind is isotropic (dashed lines) or an
  anisotropic photoevaporation flow. The solid lines shows a wind with a
  moderate degree of anisotropy $(k=0.5)$, which is expected for the proplyds.
  And the dooted lines show a wind with extreme anisotropy degree $(k=8)$.}
\label{fig:r-beta}
\end{figure}

@@

Beneath the error margins, our measurements are consistent with \citet{Robberto:2005} for $R'_0/D$. From figure (\ref{fig:conic-xi}), we also
note that the LV4 measurements fits better with models where its photoevaporated flow is isotropic. The same is true with \citet{Robberto:2005} data.The rest of the proplyds fit better with more anisotropic winds, which may explain why \citet{Robberto:2005} did not find a match between models
and data, since they only showed models where the interacting winds are isotropic.

@@

%\begin{figure}
%\includegraphics[width=\linewidth]{../../read-shapes/proplyd-shell-R0-Rc-cloud} 
%\label{fig:prop-shell-rad}
%\caption{Measurements of proplyd's characteristic radii $R_c$ and $R_0$. The curves represent a single bow shock with  fixed wind's momentum ratio $\beta$. 
%The dots represent separations in inclination of $15^{\circ}$. The semitransparent curves represent bow shocks which the inner wind is isotropic and the full colored 
%curves bow shocks which inner wind density decays as $\cos^{1/2}\theta$. The observational measurements are accompained with radial bars which represents the variations 
%with a fraction of the shell's marks removed. Proplyds with less data marks or high asymmetry show higher deviations in the measurements.
%Our measures match far better than \citep{Robberto:2005}, but our data tend to lie at high inclinations $i \gtrsim 45^\circ$, when we expected the opposite. Right side: The same
%}
%\end{figure}

@@

With this we can use the results of section \ref{sec:conic} to estimate the projected conic shapes for bow shocks with different winds 
momenta and different density distributions. 
In figure (\ref{fig:conic-xi}) we show the theoretical conic curves for different vales of $\beta$ with a fixed $\xi$. Most of the proplyds fit well 
with a elliptic-like conic shape and moderate to high degree of anisotropy of their wind.
LV4 is a special case which fits better with an hyperbola and isotropic wind.

\begin{figure*}
\begin{tabular}{cc}
\includegraphics[width=0.48\linewidth]{../../read-shapes/conic_xi-10} & \includegraphics[width=0.48\linewidth]{../../read-shapes/conic_xi-08} \\
\includegraphics[width=0.48\linewidth]{../../read-shapes/conic_xi-04} & \includegraphics[width=0.48\linewidth]{../../read-shapes/conic_xi-02} 
\end{tabular}
\label{fig:conic-xi}
\caption{Measurements of proplyd's characteristic radii $R_c$ and $R_0$. The curves represent a conic-like bow shock with 
fixed momentum ratio $\beta$ and the derived value of $\theta_c$ is also shown.The dots along each curve represent separation in inclination of 
$15^\circ$. The measurements of each proplyd are accompained with the set of variations represented as colored radial lines. In 
each graph we use a different degree of the weaker wind anisotropy, starting from an isotropic wind $(\xi=1)$, to the most anisotropic wind
$(\xi=0.2)$.}
\end{figure*}
%Measurements of proplyd's characteristic radii $R_c$ and $R_0$. The curves represent a single bow shock with fixed wind's momentum ratio $\beta$. 
%The dots represent separations in inclination of $15^{\circ}$. The semitransparent curves represent bow shocks which the inner wind is isotropic and the full colored 
%curves bow shocks which inner wind density decays as $\cos^{1/2}\theta$. The observational measurements are accompained with radial bars which represents the variations 
%with a fraction of the shell's marks removed. Proplyds with less data marks or high asymmetry show higher deviations in the measurements.
